module2extra

### 2022-03-14 module2extra.Rmd
Terre's suggestion

---
title: "module2extra"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "module2extra"
output:
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

```{r}

likertmodule2 <- module2%>%
  filter(!row_number() %in% c(1,2)) %>% 
  select(starts_with("Ben"))%>%
  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene)%>%
  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
  select(-Ben) %>% 
  group_by(Technology, Perceived_Benefit) %>%
  dplyr::summarise(n=n())%>%
  mutate(Perceived_Benefit = factor(Perceived_Benefit,  levels = c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")))%>%
  pivot_wider(names_from = Perceived_Benefit, values_from = n)%>%
  rename("NA1"="Rather not say/Don't know")%>%
  select("Technology","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial", "NA1","NA")%>%
  unite("Rather not say/Don't know", "NA1":"NA", na.rm = TRUE, remove = FALSE)%>%
  select(!c("NA1","NA"))

```

```{r}
#summary statistics for nuclear energy accept, reject and reluctantly accept scale
codedmodule2 %>%
  summarize_at(vars(N_accept,N_reject,N_reluctantlyaccept), list(~mean(., na.rm = TRUE),~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE),~n())) %>%
  add_rownames() %>%
  gather(acceptance, value, -rowname) %>%
  separate(acceptance, c("N_accept", "var") ,  extra = "merge", fill = "left") %>%
  separate(var, c("Acceptance", "summary")) %>%
  spread(summary, value) %>%
  select(-rowname, -N_accept)%>%
  arrange(mean)

```

```{r}

# chi square test for risk perception from nuclear energy and gender, race

# first combine gender and caste variables

chitest <- codedmodule2 %>%
  select(Risky_Nuclear,Risky_Hydro, Risky_Hydro, Risky_Solar,Urban_Rural, Gender, Caste) %>%
  na.omit() %>%
  filter(!Caste=="Rather not say/Don't know")%>%
  unite(gendercaste, Gender, Caste, sep = "_", remove = FALSE)

chitest

```
